# First Try: NaiveBayes

## read train.csv into dataframe
```{r}
df <- read.csv("Titanic/train.csv",na.strings = "")
```

##Check the datatypes
```{r}
str(df)
```

## convert Survived column and Pclass column to factors
```{r}
df$Survived<- as.factor(df$Survived)
df$Pclass<- as.factor(df$Pclass)
```

##summary
```{r}
summary(df)
```

## remove from df : PassengerId, Name, Ticket, Cabin. we decided to remove Cabin bacuse of the many N/A values and see that it really help to get better accuracy
```{r}
df <- df[,-c(1,4,9,11)]
```

##Split the data into train and test sets
```{r}
indices <- sample(1:nrow(df),nrow(df)*0.8)
traindf<- df[indices,]
testdf<- df[-indices,]
```

#load e1071 library and invoke naiveBayes method
#Train the model based on the train set:
```{r}
#install.packages('e1071')
library(e1071)
nb_model <- naiveBayes(Survived~.,data = df)
```

## read train.csv into new dataframe
```{r}
new_df <-read.csv('Titanic/test.csv',na.strings = "")
```

## save PassengerId
```{r}
ids<- new_df$PassengerId
```

## convert Survived column and Pclass column to factors
```{r}
new_df$Pclass<- as.factor(new_df$Pclass)
```

## remove from df : PassengerId, Name, Ticket, Cabin. we decided to remove Cabin bacuse of the many N/A values and see that it really help to get better accuracy
```{r}
new_df<- new_df[,-c(1,3,8,10)]
```

##predict servived using the trained model
```{r}
pred <- predict(nb_model,new_df,na.action = na.pass)
```

## bind PassengerId to the servived prediction & write result to .csv file
```{r}
submit <- data.frame(PassengerId =ids, Survived = pred)
write.csv(submit, file = "naive_base.csv", row.names = FALSE)
```