
```{r}
dfTrain <- read.csv("Titanic/train.csv",na.strings = "")
dfTest <- read.csv("Titanic/test.csv",na.strings = "")
```


# Load required packages
```{r}
library(rpart)
library(randomForest)
library(party)
```


# Join together the test and train sets for make pred for NAs fields
```{r}
dfTest$Survived <- NA
combind <- rbind(dfTrain, dfTest)
```


# Convert Name to a string
```{r}
combind$Name <- as.character(combind$Name)
```


# Create new variable: Title
```{r}
combind$Title <- sapply(combind$Name, FUN=function(x) {strsplit(x, split='[,.]')[[1]][2]})
combind$Title <- sub(' ', '', combind$Title)
```


# Combind small grupe of titles to one gruop
```{r}
combind$Title[combind$Title %in% c('Mme', 'Mlle')] <- 'Mlle'
combind$Title[combind$Title %in% c('Dona', 'Lady', 'the Countess', 'Jonkheer')] <- 'Lady'
combind$Title[combind$Title %in% c('Capt', 'Don', 'Major', 'Sir')] <- 'Sir'
```


# Convert to a factor
```{r}
combind$Title <- factor(combind$Title)
```


# Fill in Age NAs with rpart for better predict
```{r}
Agefit <- rpart(Age ~ Pclass + Sex + SibSp + Parch + Fare + Embarked + Title,
                data=combind[!is.na(combind$Age),], method="anova")
combind$Age[is.na(combind$Age)] <- predict(Agefit, combind[is.na(combind$Age),])
```


# Fill in Fare NAs with rpart for better predict
```{r}
Farefit <- rpart(Fare ~ Pclass + Sex + SibSp + Parch + Age + Embarked + Title,
                data=combind[!is.na(combind$Fare),], method="anova")
combind$Fare[is.na(combind$Fare)] <- predict(Farefit, combind[is.na(combind$Fare),])
```


# Split Again to test and train 
```{r}
train <- combind[1:891,]
test <- combind[892:1309,]
```


# Build Random Forest
```{r}
fit <- cforest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title,
               data = train, controls=cforest_unbiased(ntree=2000, mtry=5)) 
```


# Bind PassengerId to the servived prediction and make csv
```{r}
Prediction <- predict(fit, test, OOB=TRUE, type = "response")
submit <- data.frame(PassengerId = test$PassengerId, Survived = Prediction)
write.csv(submit, file = "forest.csv", row.names = FALSE)
```
